Ampersand uses Relation Algebra as Programming Language

### 2017-07-11 2017 JLAMP/articleRamics.tex
process some remarks from Wolfram

	By using the absorption property
\begin{equation}
s-(s\cap x)=s-x\label{absorb x}
\end{equation}
	it is obvious that $(r\cup \Delta)\backslash(r;s)$ is a solution too.
	Even though this solution may contain more pairs, it is equivalent to the minimal solution.

@@

\subsection{Further Research}
\label{sct:Further Research}
	Further research on this topic is required to bring relation algebra still closer to the community of practitioners.
	Further use of relation algebra can be made by incorporating a model checker, such as the Alloy analyser~\cite{Alloy2006}, to detect inconsistent rules.
	An exciting new development is Amperspiegel~\cite{Amperspiegel}, which brings notational flexibility at the fingertips of the user.
	Developments in the Ampersand-compiler are going towards a rule-repository (written in Ampersand itself).
	This will make collaborative information systems development in Ampersand easier, because the repository can assist in automating
	the software development process further.
	Other research is needed towards a comprehensive theory of information systems.
	Currently, there is no theory (in the mathematical meaning of the word) for information systems.
	In the Ampersand project, a sub-project called ``Formal Ampersand'' is being conducted to achieve this goal.
\bibliographystyle{spmpsci}
\bibliography{doc}

>>>>

	By using the absorption property
\begin{equation}
s-(s-x)=s\cap x\label{absorb x}
\end{equation}
	it is obvious that $(r\cup \Delta);(s\cap(r\cup \Delta)\backslash(r;s))\ \subs\ r;s$ is equivalent to equation~\ref{eqn:ins r del s}. Therefore, it yields an equivalent solution.

@@

\subsection{Further Research}
\label{sct:Further Research}
	Further research on this topic is required to bring relation algebra still closer to the community of practitioners.
	Further use of relation algebra can be made by incorporating a model checker, such as the Alloy analyser~\cite{Alloy2006}, to detect inconsistent rules.
	An exciting new development is Amperspiegel~\cite{Amperspiegel}, which brings notational flexibility at the fingertips of the user.
	Developments in the Ampersand-compiler are going towards a rule-repository (written in Ampersand itself).
	This will make collaborative information systems development in Ampersand easier, because the repository can assist in automating
	the software development process further.
	Other research is needed towards a comprehensive theory of information systems.
	Currently, there is no theory (in the mathematical meaning of the word) for information systems.
	In the Ampersand project, a sub-project called ``Formal Ampersand'' is being conducted to achieve this goal.
\subsection{Acknowledgements}
\label{sct:Acknowledgements}
	Firstly, I wish to thank Sebastiaan Joosten for introducing me to Isabelle and for inspiring me with his challenging critiques.
	I owe many thanks to Wolfram Kahl, Michiel Stornebrink, Han Joosten, and the anonymous reviewers of RAMiCS for their useful feedback.
	And I am grateful to the Open University and Ordina for funding this research.
\bibliographystyle{spmpsci}
\bibliography{doc}
